PyPy: raising the level for Dynamic Language implementations

### 2007-05-27 talk/dyla2007/dyla.tex
I find "fact" a bit strong here.

The fact that limitations of a C-based implementation of a dynamic
language leads to the emergence of additional implementations is clear
in the case of Python.  The reference implementation, \implname{CPython}
\cite{cpy251}, is a simple recursive interpreter.  \implname{Stackless
Python} \cite{stackless} is a fork that adds micro-threading
capabilities to Python. One of the reasons for not incorporating it back
into CPython was that it was felt that they would make the
implementation too complex. Another implementation of the Python
language is \implname{Psyco} \cite{psyco-software}, which adds a
JIT-compiler to CPython.  Finally, \implname{Jython} is a
re-implementation for the Java VM and \implname{IronPython} one for
.NET.  All of these need to be kept in sync with the relatively fast
evolution of the language.

>>>>

The observation that limitations of a C-based implementation of a dynamic
language leads to the emergence of additional implementations is clear
in the case of Python.  The reference implementation, \implname{CPython}
\cite{cpy251}, is a simple recursive interpreter.  \implname{Stackless
Python} \cite{stackless} is a fork that adds micro-threading
capabilities to Python. One of the reasons for not incorporating it back
into CPython was that it was felt that they would make the
implementation too complex. Another implementation of the Python
language is \implname{Psyco} \cite{psyco-software}, which adds a
JIT-compiler to CPython.  Finally, \implname{Jython} is a
re-implementation for the Java VM and \implname{IronPython} one for
.NET.  All of these need to be kept in sync with the relatively fast
evolution of the language.
